Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2017-03-01 websci-2017/source/paper.tex
more updates.

An alternative assumption might be that each hop away from Alice in
in the network,
reduces the probability that a node can resist compromise exponentially.
Such a situation might occur because nodes more distant from Alice may be
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, and less likely to take proactive security measures against that
adversary.
The above model can be further
approximated by assuming that nodes up to some fixed number
of hops cannot be compromised, and those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define it formally.

@@

We can allow for more realistic transitivity assumptions and incorporate
network structure into a trust model with one key insight:
even if no single path between a sender and receiver is fully trusted,
multiple copies of a message can be sent along different paths and compared
by the receiver to detect and correct errors.
However, in the presence of an attacker, there is only benefit in sending an
additional message along a path if that path does not share untrusted
single points of failure with any of the existing message paths
(otherwise, the adversary can compromise both messages
by causing a single fault).
Following \cite{reiter_resilient_1998},
we call paths that do not share any untrusted single points of failure
{\em independent}.
The maximum number of independent paths represents the effective redundancy that
can be utilized by any redundancy-based fault tolerance scheme.

We now propose a method for quantifying the effective redundancy of a network
as a function of its structure and level of trust transitivity.
For the purpose of analyzing adversarial fault tolerance,
this method allows a communication network
to be modeled as a set of virtual channels that directly
connect each node pair,
with each virtual channel providing some level of redundancy.

>>>>

An alternative assumption might be that each hop away from Alice in
in the network
reduces the probability that a node can resist compromise exponentially.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, and less likely to take proactive security measures against that
adversary.
The above model can be further
approximated by assuming that nodes up to some fixed number
of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define it formally.

@@

\subsection{Effective Redundancy}

We now propose a method for quantifying the effective redundancy of a network
as a function of its structure and level of trust transitivity.
For the purpose of analyzing adversarial fault tolerance,
this method allows us to model each pair of nodes
in a complex communication network
as being directly connected by a dedicated {\em virtual channel}
that provides some level of redundancy.
